---
title: "Sink_Strength.Rmd"
author: "Rachel Carlson"
date: "3/10/2022"
output: html_document
---

```{r setup, include=FALSE}
#Read in packages 
library(ncdf4)
library(lubridate)
library(ggplot2)
library(ggquiver)
library(dplyr)
library(maptools)
library(sf)
```

This Rmd demonstrates how to ingest .nc files from Parcels and turn output into a sink strength metric for pre-determined larval settlement sites. First code segments are adapted from Gabi Mukai.

## 1. Ingest Parcels output

```{r}
# Ingest .nc file from Parcels output
dat <- nc_open('/Users/rachelcarlson/Documents/Research/Larvae/Data/Primary/parcels/out/Test_Larvae_12Feb2022.nc')
# Load settlement site points
sites <- read.csv("/Users/rachelcarlson/Documents/Research/Larvae/Data/Primary/parcels/kona_larvae/tile_sites.csv")

# Extract variables from .nc file (ncdf4 package)
lo <- ncvar_get(dat, 'lon')
la <- ncvar_get(dat, 'lat')
i <- ncvar_get(dat, 'trajectory')
t  <- ncvar_get(dat, 'time') 
tunit <- dat$var$time$units
c.distance <- ncvar_get(dat, 'distance')
nc_close(dat)
```

## 2. Map particle paths as continuous lines
#### 2.i Create a dataframe/sf object from output

Parcels output takes the form of points every 6 hours, or whatever other timestep you choose (i.e., each parcel's position is recorded each 6 hours). These points need to be converted to a multiline in order to see if the particle paths intersect settlement sites. To do this, convert .nc output to a dataframe.

```{r}
# Fetch any variables you want to be in the dataframe and convert to vector
tvec <- as.vector(t)
# age <- as.vector(a)
id <- as.vector(i)
coord1 <- as.vector(lo) - 360 # Remember: since particle data is now in 0 - 360 dd (rather than -180 to 180), we need to convert locations accordingly. It would be easier to just convert settlement site to 0 - 360, but adding a buffer automatically reprojects that data.
coord2 <- as.vector(la)
# site.no <- as.vector(site.no) # Origin site, will use this later for origin probability mapping
cum_distance <- as.vector(c.distance)

# Merge data to create dataframe
traj <- data.frame(tvec, coord1, coord2, cum_distance)

# Attribute data to particle number
ntraj <- dim(lo)[2] # number of particles/individual trajectories (37)
ntime <- dim(lo)[1] # number of points per particle (41 - i.e., points logged for each particle every 6 hours for 10 days)
traj$particle <- rep(1:ntraj, each=ntime) # Add a column to the dataframe of 41 "particle 1s", then 41 "particle 2s", etc.
```

#### 2.ii Transform dataframe to linestring

The dataframe contains a collection of points for each particle. Transform these points into a continuous path.

```{r}
line1 <- traj[,c(-1,-4)] %>% # remove variables you don't need (alternatively, can aggregate into one value/path using `summarize`)
  sf::st_as_sf(coords = c("coord1", "coord2")) %>%
  sf::st_set_crs(4326) %>% 
  group_by(particle) %>% 
  summarize(do_union = FALSE) %>% # This is important: without this, points will be connected at random and you'll get a zigzag
  sf::st_cast("LINESTRING")

# Check to make sure the geometries/paths look good
plot(line1$geometry)
```

## 3. Intersect with settlement sites

Determine whether each particle path crossed settlement sites.

```{r}
# Convert to sf point object
sites <- sites %>%
  st_as_sf(coords = c("lon","lat")) %>% 
  st_set_crs(4326)
write_sf(sites, "/Users/rachelcarlson/Desktop/foo2.shp")
# Buffer sites by 100 m (select best buffer)
sites100 <- st_buffer(sites, 100) %>% st_transform(crs = 4326)
sites100$site <- as.character(sites100$site)

# Find intersections between lines and buffered site polygons
inter <- st_intersects(sites100, line1) # sites goes first, so will list all paths intersecting each site
inter
```






